Secure Composition of Robust and Optimising Compilers

### 2023-07-10 popl/main.tex
proof sketch

The proof of \Cref{thm:cca:rtp:tms} uses standard techniques in secure compilation literature.
These techniques are also used for similar theorems in this paper.

>>>>

The proof of \Cref{thm:cca:rtp:tms} uses standard techniques in secure compilation literature that are also used for similar theorems in this paper.
